The impact of cosmic variance on simulating weak lensing surveys

### 2014-12-01 Writeup/paper_v3.tex
more stuff from discussion w/ henk

\rachelnew{However, it is important to bear in mind that the method
  proposed in \cite{2013MNRAS.432.2385S} involves determining not just
a redshift-dependent correction but also a type-dependent colour
gradient correction, which could partially mitigate the effects of the
environment dependence seen here.  We showed in
Sec.~\ref{sec:mitigation} that a simple type-dependent split does not
remove the effects of environment on the intrinsic ellipticity
distribution, but testing whether it (or a more complex type split) is
enough to remove the effects of colour gradients in Euclid is a more
complicated analysis that is beyond the scope of this work.} It seems that a future study using
  an {\em HST} field with more than one band would be warranted, to
  test whether the \rachelnew{ possible} discrepancy between our findings and those of
  \cite{2013MNRAS.432.2385S} arises from a weak connection between
  colour gradients and $B/T$ (meaning that our results do not imply a
  problem with colour gradient calibration), \rachelnew{or whether a
    division into several galaxy types is truly enough to remove the colour
    gradient effect, verifying the conclusions of
    \cite{2013MNRAS.432.2385S} using synthetic galaxy models}.}

>>>>

\rachelnew{However, it is important to bear in mind that the method
  proposed in \cite{2013MNRAS.432.2385S} involves determining not just
a redshift-dependent correction but also a type-dependent colour
gradient correction, which could partially mitigate the effects of the
environment dependence seen here.  Moreover, the colour gradient
effect is higher order than the intrinsic ellipticity distribution,
and thus may be less susceptible to systematics due to the
environmental effects considered here.   We showed in
Sec.~\ref{sec:mitigation} that a simple type-dependent split does not
remove the effects of environment on the intrinsic ellipticity
distribution, but testing whether it (or a more complex type split) is
enough to remove the effects of colour gradients in Euclid is a more
complicated analysis that is beyond the scope of this work.} It seems that a future study using
  an {\em HST} field with more than one band would be warranted, to
  test whether \rachelnew{or not our results suggest a discrepancy with those
    of 
  \cite{2013MNRAS.432.2385S}.  It is possible that the connection between
  colour gradients and $B/T$ is weak enough that our results do not imply a
  problem with colour gradient calibration, or that 
    division into several galaxy types or colours is truly enough to remove the colour
    gradient effect due to its being a higher order effect, consistent with the findings of 
    \cite{2013MNRAS.432.2385S} using synthetic galaxy models}.}
